Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity

### 2025-10-08 paper_short_in_one.tex
update the auto-generated paper_short_in_one.tex file

@@

Addressing underdiagnosis of Chagas disease through scalable ECG-based screening is the focus of the 2025 George B. Moody PhysioNet Challenge \cite{goldberger2000physionet, cinc2025}. Enabled by aggregated multi-cohort ECG datasets \cite{ribeiro2020automatic, Cardoso_2016_Sami-Trop, wagner2020ptb_xl, Nunes_2021_Incidence, Filho_2020_Prognostic}, the Challenge frames a multi-source learning setting with heterogeneous label reliability and severe class imbalance.

@@

\begin{figure*}[!t]
\centering
\begin{tikzpicture}[
    % font=\small,
    line width=0.75pt,
    >={Latex[length=3mm]},
    node distance=6.4mm,
    every node/.style={inner sep=2pt},
    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=blue!10},
    block/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=12mm,
                  align=center, fill=orange!12},
    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
               align=center, fill=green!12},
    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=cyan!10},
    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=purple!10},
    output/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                align=center, fill=red!10},
    arrow/.style={-{Latex[length=3mm]}, thick},
    darr/.style={-{Latex[length=2.4mm]}, thick},
    dashedarrow/.style={-{Latex[length=2.6mm]}, thick, dashed},
    ann/.style={inner sep=1pt, align=center},
    layer/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=blue!6},
    bnact/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=violet!10},
    act/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=red!10},
    drop/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=gray!15, dashed},
    sum/.style={draw, circle, inner sep=1.6pt, fill=white},
    % brace/.style={decorate, decoration={brace, amplitude=6pt}},
    detailbox/.style={draw, rounded corners=3pt, inner sep=6pt, fill=orange!3}
]

% ================= Left (overall vertical path) =================
\node[stem] (input) {Input \\ (12$\times$L)};
\node[stem, below=of input] (stem) {Stem \\ Conv ks=15 \\ BN + ReLU \\ 64 Ch};

@@

% ================= Right (expanded single bottleneck internals) =================
% Anchor for expansion (to the right of overall bottleneck block)
\coordinate (expandAnchor) at ($(input.east)+(45mm,0)$);

@@

\caption{Model architecture. Left: overall network: a stem (Conv1d, kernel size (ks) 15, 64 channels (Ch), Batch Normalization (BN), ReLU) followed by four bottleneck residual blocks, a global squeeze-and-excitation (SE) module, global max pooling, and an MLP head producing $C = 2$ logits. Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded channels.
Right: internal bottleneck structure (1--15--1 pointwise--temporal--pointwise). The middle convolution of kernel size 15 uses a stride of 4 for temporal downsampling; kernel size 1 convolutions reduce and then expand channels, and a projection convolution (kernel size 1, stride 4) aligns resolution and width for the residual path. For clarity, dropout layers present in the implementation are omitted. Abbreviations: ks kernel size; Ch channels; BN Batch Normalization; SE squeeze-and-excitation; MLP multi-layer perceptron.}
\label{fig:model}
\end{figure*}

@@

The Challenge score of our team ``Revenger'' on the hidden test set was 0.163, ranking 32nd among 40 teams eligible for rankings. The score on the internal hold-out of the public training data, the hidden validation score, and the validation ranking are summarized in Table~\ref{tab:scores}.

\begin{table}[!htp]
\centering
% \input{tables/official_phase_results}
\begin{tabular}{r|r|r|r}
Training          & Validation & Test & Ranking   \\ \hline
$0.451 \pm 0.005$ & 0.245      & 0.163  & 32~/~40 \\ \hline
\end{tabular}

\caption{Challenge scores for our submitted entries (team ``Revenger''). Training: internal hold-out mean $\pm$ std over repeated runs. Validation: best among 10 validation submissions. Test: to be announced. Ranking: position on the hidden validation leaderboard.}
\label{tab:scores}
\end{table}

>>>>

\usepackage{adjustbox}

@@

Addressing underdiagnosis of Chagas disease through scalable ECG-based screening is the focus of the 2025 George B. Moody PhysioNet Challenge \cite{goldberger2000physionet, 2025ChallengeCinC, 2025ChallengePreprint}. Enabled by aggregated multi-cohort ECG datasets \cite{ribeiro2020automatic, Cardoso_2016_Sami-Trop, wagner2020ptb_xl, Nunes_2021_Incidence, Filho_2020_Prognostic}, the Challenge frames a multi-source learning setting with heterogeneous label reliability and severe class imbalance.

@@

\begin{figure*}[!t]
\centering
\adjustbox{width=0.70\linewidth}{
\begin{tikzpicture}[
    % font=\small,
    line width=0.75pt,
    >={Latex[length=3mm]},
    node distance=6.4mm,
    every node/.style={inner sep=2pt},
    stem/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=blue!10},
    block/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=12mm,
                  align=center, fill=orange!12},
    se/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
               align=center, fill=green!12},
    pool/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=cyan!10},
    head/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                 align=center, fill=purple!10},
    output/.style={draw, rounded corners=2pt, minimum width=30mm, minimum height=9.5mm,
                align=center, fill=red!10},
    arrow/.style={-{Latex[length=3mm]}, thick},
    darr/.style={-{Latex[length=2.4mm]}, thick},
    dashedarrow/.style={-{Latex[length=2.6mm]}, thick, dashed},
    ann/.style={inner sep=1pt, align=center},
    layer/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=blue!6},
    bnact/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=violet!10},
    act/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=red!10},
    drop/.style={draw, rounded corners=2pt, minimum width=19mm, minimum height=6.2mm,
                  align=center, fill=gray!15, dashed},
    sum/.style={draw, circle, inner sep=1.6pt, fill=white},
    % brace/.style={decorate, decoration={brace, amplitude=6pt}},
    detailbox/.style={draw, rounded corners=3pt, inner sep=6pt, fill=orange!3}
]

% ================= Left (overall vertical path) =================
\node[stem] (input) {Input \\ (12$\times$L)};
\node[stem, below=of input] (stem) {Stem \\ Conv ks=15, 64 Ch \\ BN + ReLU};

@@

% ================= Right (expanded single bottleneck internals) =================
% Anchor for expansion (to the right of overall bottleneck block)
\coordinate (expandAnchor) at ($(input.east)+(50mm,0.2)$);

@@

}
\caption{Model architecture. Left: overall network: a stem (Conv1d, kernel size 15, 64 output channels, Batch Normalization, ReLU) followed by four bottleneck residual blocks, a global SE module, global max pooling, and an MLP head producing $C = 2$ logits. Channel widths shown ($512 \to 768 \to 1024 \to 1280$) are the expanded channels.
Right: internal bottleneck structure. The middle convolution of kernel size 15 uses a stride of 4 for temporal downsampling; kernel size 1 convolutions reduce and then expand channels, and a projection convolution (kernel size 1, stride 4) aligns resolution and width for the residual path. For clarity, dropout layers present in the implementation are omitted. Abbreviations: ks kernel size; Ch channels; BN Batch Normalization; SE squeeze-and-excitation; MLP multi-layer perceptron.}
\label{fig:model}
\end{figure*}

@@

The Challenge score of our team ``Revenger'' on the hidden test set was 0.163, ranking 32nd among 40 eligible teams. This score and ranking, along with extra scores on the internal hold-out of the public training data, and on the hidden validation set, are summarized in Table~\ref{tab:scores}.

\begin{table}[!htp]
\centering
% \input{tables/official_phase_results}
\begin{tabular}{r|r|r|r}
Training          & Validation & \textbf{Test}  & \textbf{Ranking} \\ \hline
$0.451 \pm 0.005$ & 0.245      & \textbf{0.163} & \textbf{32~/~40} \\ \hline
\end{tabular}

\caption{Challenge scores for our submitted entries (team ``Revenger''). Training: internal hold-out mean $\pm$ std over repeated runs. Validation: best among 10 validation submissions. Test: the unique test submission. Ranking: position on the hidden test leaderboard.}
\label{tab:scores}
\end{table}
